A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Remove Ethereum introduction

\subsection{Enable Automated Trading Process}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract that can make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address and DID document address of the data provider, subscription and brokerage fee, MAM channel/endpoint ID (the data entry point), and the broker-certified encryption key are listed on Product Contract. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.

>>>>

\subsection{Enable Automated Trading Process}
Ethereum smart contract can make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures. Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream. The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.
